A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-21 4_method.tex
redo overview

\section{Method}
\subsection{Overview}

The naive method consists of consecutive inward offsets from the outline.

These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones with \SI{45}{\degree} touching the input shape.
The constant width insets are then conceptualized as the intersection between the Union of Cones (UoC) and horizontal planes at regular intervals.

Alternatively: the MAT captures the internal part of the distance field and the constant width insets are the isocontours of the that distance field.

The problem with the constant width insets is that in the center of the shape \todo{it doesn't fit}.
because the distance to the boundary is not an integer multiple of the nozzle size.
We therefore change the mesh such that an exact integer beads will be generated.

A simplified version of our framework can be conceptualized as such:
\begin{itemize}
\item Compute the mesh representing the Union of Cones (UoC) for the input shape
\item Round the heights of central nodes to to the nearest slicing height
\item Smooth out sharp transitions between regions with different integer multiple slice heights
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

\begin{figure}
\centering
\setlength{\figwidth}{.3\columnwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_mat.png}
\includegraphics[width=\columnwidth]{sources/method/surface/naive.pdf}
\caption{Union of Cones}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_no_transitions.png}
\includegraphics[width=\columnwidth]{sources/method/surface/no_transitions.pdf}
\caption{Rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_st.png}
\includegraphics[width=\columnwidth]{sources/method/surface/distributed.pdf}
\caption{Smoothed}
\end{subfigure}
\caption{
A simplified geometrical conceptualization of our framework.
The 3D surface representations (top) are sliced into the toolpaths (bottom) which fill the outline shape.
We first compute the Union of Cones mesh, then alter it to prevent shallow slopes and then smooth it to prevent instantaneous changes.
}
\label{3d_surface_overview}
\end{figure}

problems

Not all non-outline nodes are central.
How to determine the height of such nodes?

\Cref{section_toolpath_extraction} shows how we can determine the heights of non-central verts, extends the simplified method to a generalized framework and provides an efficient algorithm to slice the modified UoC.

\todo{OLD: }
When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
We decide on a bead count at locations which lie in central positions of the shape and apply an optimal distribution of widths from the central regions outward.

What constitutes an optimal distribution is governed by a beading strategy.
Our framework allows for different beading strategies which can optimize for different criteria.
A beading strategy is defined by several several functions which govern the behavior of our framework.

\begin{enumerate}
\item Compute a skeleton of the outline shape.
\item Use a significance measure to mark regions of the skeleton which are central.
\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the extrusion beads.
\end{enumerate}
See \cref{overview_fig}.

@@

@@

\subsection{Surface construction}
\todo{TODO: explain section title!}

The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
Starting from the medial axis we further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.

@@

\subsection{Center classification}
\todo{TODO: explain section title!}

@@

\subsection{Central height adjustment}
\todo{TODO: explain section title!}

@@

\subsection{Peripheral height adjustment}
\label{section_toolpath_extraction}

>>>>

\section{Method}
\subsection{Overview}
The naive method consists of consecutive inward offsets from the outline using a constant bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones of \SI{45}{\degree} which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}

For the naive method the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
We therefore change the UoC mesh such that an exact integer beads will be generated in the center.
More specifically, we round the height to the nearest multiple of \emph{half} the nozzle size.
That way we allow for an odd number of beads to be placed between the two sides of the outline shape.

Our technique consists of the folowing steps:
\begin{itemize}
\item Compute the mesh representing the Union of Cones (UoC) for the input shape
\item Identify central regions of the UoC
\item Round the heights of central nodes to to the nearest slicing height
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

\begin{figure*}
\centering
\setlength{\figwidth}{.18\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}

\vspace{\tempheight}

\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
\caption{Union of Cones}\label{3d_surface_overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}

\vspace{\tempheight}

\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
\caption{Center}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}

\vspace{\tempheight}

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Rounded}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

\vspace{\tempheight}

\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
\caption{Smoothed}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}

\vspace{\tempheight}

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions blue \subref{3d_surface_overview_center}
and round the height values to the nearest integer muliple of half the nozzle width \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
}
\label{3d_surface_overview}
\end{figure*}

We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

For ease of reference we have included a legend explaining the vocabulary employed in this manuscript in \cref{legend}.

@@

\iffalse

@@

\fi

\subsection{Surface construction}\label{sec_surface_construction}
The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
Starting from the medial axis we further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.

@@

\subsection{Center classification}\label{sec_center_classification}
\todo{TODO: explain section title!}

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
\todo{TODO: explain section title!}

@@

\subsection{Peripheral height adjustment}\label{sec_peripheral_height_adjustment}
